---
title: "DXA : Analyses statistiques"
author: Jérôme Pasquier (Unisanté)
date: 3 mars 2021
geometry: margin=2cm
output:
  pdf_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}

library(readxl)
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(stargazer)

opts_chunk$set(echo = FALSE)

# Import data
dxa <- read_xlsx("../data-raw/COOL-OsteoLaus for stat (clean).xlsx",
                 sheet = "COOL data")
dxa <- as.data.frame(dxa)
dxa <- dxa[!(dxa$Id %in% c("Dx00000255", "Dx00001488")), ]
#dxa$`Follow-up DXA Years...16`
#dxa$`Follow-up DXA Years...17`

# Recode variables
for (v in names(dxa)) {
  x <- dxa[[v]]
  if (is.character(x)) {
    x <- trimws(x)
    if (all(is.na(x) | grepl("^[0-9]+((\\.|,)[0-9]+)?$", x))) {
      x <- sub(",", "\\.", x)
      x <- as.numeric(x)
    }
    dxa[[v]] <- x
  }
}
rm(v, x)
dxa$DXA_Date <- as.Date(dxa$DXA_Date, format = "%d/%m/%Y")
dxa$`Date Bariatric surgery` <- 
  as.Date(dxa$`Date Bariatric surgery`, format = "%d/%m/%Y")

# Help function(s)
getfml <- function(fit) {
  as.character(fit$call$formula) %>% {paste(.[2], .[1], .[3])}
}

```

<!-- ====================================================================== -->

# Analyses descriptives

## Variables continues

```{r, echo=FALSE}

V <- c("weight_preOp", "Follow-up DXA months", "weight loss kg",
       "Total weight loss (TWL)", "Excès weight loss", "Nadir weight",
       "Time Nadir weight (months)")
do.call(rbind, lapply(V, function(v) {
  x <- na.omit(dxa[[v]])
  data.frame(
    variable = v,
    n = length(x),
    mean = mean(x),
    sd = sd(x),
    median = median(x),
    q25 = quantile(x, 0.25),
    q75 = quantile(x, 0.75),
    min = min(x),
    max = max(x)
  )
})) %>%
  kable(digits = 2, row.names = FALSE)
rm(V)

```

## Variables binaires

```{r, echo=FALSE}

V <- c("T2D-PreOp", "HTA-PreOp", "Dyslipidemia-PreOp", "T2D-PostOp",
       "HTA-PostOp", "Dyslipidemia-PostOp", "TTT_DT2 PostOp",
       "TTT_lipid PostOp")
do.call(rbind, lapply(V, function(v) {
  x <- na.omit(dxa[[v]])
  if (!all(is.na(x) | x %in% 0:1)) stop(paste(v, "not binary"))
  data.frame(
    variable = v,
    n = length(x),
    npos = sum(x),
    `prop (%)` = mean(x) * 100,
    check.names = FALSE
  )
})) %>%
  kable(digits = 2, row.names = FALSE)
rm(V)

```

<!-- ====================================================================== -->

# Analyses de régression

```{r, echo=FALSE}

rename_matrix <- matrix(byrow = TRUE, ncol = 2, c(
  "DX03_age",                          "DX03_Age",
  "DX06_BMI",                          "DX06_BMI",
  "Total weight loss (TWL)",           "TotalWeightLoss", 
  "Excès weight loss",                 "ExcessWeightLoss",
  "DX58_LeanMassTot%",                 "DX58_LeanMassTotPercent",
  "DX62_ALMI (indice de masse maigre appendiculaire ajusté)", "DX62_ALMI",
  "Nadir weight",                      "NadirWeight",
  "DX55_Tissu adipeux viscéral (VAT)", "DX55_VAT",
  "T2D-PreOp",                         "T2DPreOp",
  "HTA-PreOp",                         "HTAPreOp",
  "Dyslipidemia-PreOp",                "DyslipidemiaPreOp",
  "T2D-PostOp",                        "T2DPostOp",
  "HTA-PostOp",                        "HTAPostOp",
  "Dyslipidemia-PostOp",               "DyslipidemiaPostOp",
  "DX59_FatMassTotale%",               "DX59_FatMassTotPercent"
))
colnames(rename_matrix) <- c("Name in xlsx file", "Name in analyses")
dta <- dxa
for (i in 1:nrow(rename_matrix)) {
  names(dta)[names(dta) == rename_matrix[i, 1]] <- rename_matrix[i, 2]
}
rm(rename_matrix, i)
dta$FollowUpYears <- as.numeric(dta$DXA_Date - dxa$`Date Bariatric surgery`)
dta$FollowUpYears <- dta$FollowUpYears / 365.2425
dta$DX03_Age_C <- dta$DX03_Age - mean(dta$DX03_Age)
dta$TotalWeightLoss_C <- dta$TotalWeightLoss - mean(dta$TotalWeightLoss)
dta$ExcessWeightLoss_C <- dta$ExcessWeightLoss - mean(dta$ExcessWeightLoss)
dta$NadirWeight_C <- dta$NadirWeight - mean(dta$NadirWeight)
dta$FollowUpYears_C <- dta$FollowUpYears - mean(dta$FollowUpYears)
dta$DX59_FatMassTotPercent_C <-
  dta$DX59_FatMassTotPercent - mean(dta$DX59_FatMassTotPercent)

```

<!-- ================== Outcome: DX58_LeanMassTotPercent ================== -->

## Variable dépendante : `DX58_LeanMassTotPercent`

### Régressions univariables

```{r, fig.show="hold"}
X <- c("TotalWeightLoss", "ExcessWeightLoss", "NadirWeight", "DX03_Age",
       "FollowUpYears")
figs <- lapply(X, function(x) {
  fml <- as.formula(paste("DX58_LeanMassTotPercent ~", x))
  fit <- lm(fml, dta)
  b <- signif(coef(fit)[[2]], 3)
  ci <- signif(confint(fit)[2, ], 3)
  p <- coef(summary(fit))[2, "Pr(>|t|)" ]
  p <- if (p >= 0.001) paste0("p=", round(p, 3)) else "p<0.001"
  r2 <- paste0("R2=", round(summary(fit)$r.squared, 3))
  cap <- paste0("b = ", b, " (", ci[1], ",", ci[2], "), ", p, ", ", r2)
  fig <- ggplot(dta, aes_string(y = "DX58_LeanMassTotPercent", x = x)) +
    geom_point() +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
    labs(caption = cap, y = "LeanMassTotPrct") +
    theme(axis.title=element_text(size = rel(.75)))
})
do.call(grid.arrange, append(figs, list(ncol = 2)))
rm(X, figs)
```

```{r, fig.show="hold"}
X <- c("TotalWeightLoss", "ExcessWeightLoss")
figs <- lapply(X, function(x) {
  fml <- as.formula(paste("NadirWeight ~", x))
  fit <- lm(fml, dta)
  b <- signif(coef(fit)[[2]], 3)
  ci <- signif(confint(fit)[2, ], 3)
  p <- coef(summary(fit))[2, "Pr(>|t|)" ]
  p <- if (p >= 0.001) paste0("p=", round(p, 3)) else "p<0.001"
  r2 <- paste0("R2=", round(summary(fit)$r.squared, 3))
  cap <- paste0("b = ", b, " (", ci[1], ",", ci[2], "), ", p, ", ", r2)
  fig <- ggplot(dta, aes_string(y = "NadirWeight", x = x)) +
    geom_point() +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
    labs(caption = cap) +
    theme(axis.title=element_text(size = rel(.75)))
})
do.call(grid.arrange, append(figs, list(ncol = 2)))
rm(X, figs)
```

<!-- ================== Outcome: DX58_LeanMassTotPercent ================== -->

### Régressions multivariables - Exposition : `TotalWeightLoss`

```{r}
fits <- list(
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C * NadirWeight_C, dta),
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C * DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C * FollowUpYears_C, dta),
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C + NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C * NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ TotalWeightLoss_C * (NadirWeight_C +
       FollowUpYears_C + DX03_Age_C), dta)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]], fits[[3]],
          dep.var.labels=c("DX58LeanMassTotPercent"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[4]], fits[[5]], fits[[6]],
          dep.var.labels=c("DX58LeanMassTotPercent"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

```{r, message=FALSE, fig.show="hold"}
do.call(rbind, lapply(fits, function(fit) {
  data.frame(rstd = rstandard(fit), fml = getfml(fit))
})) %>%
  ggplot(aes(sample = rstd)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ fml, ncol = 2) +
  labs(title = "Normal Q-Q plot", x = "Theoretical Quantiles",
       y = "Standardized residuals") +
  theme(strip.text.x = element_text(size = rel(.6)))
```

<!-- ================== Outcome: DX58_LeanMassTotPercent ================== -->

### Régressions multivariables - Exposition : `ExcessWeightLoss`

```{r}
fits <- list(
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C * NadirWeight_C, dta),
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C * DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C * FollowUpYears_C, dta),
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C + NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C * NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX58_LeanMassTotPercent ~ ExcessWeightLoss_C * (NadirWeight_C +
       FollowUpYears_C + DX03_Age_C), dta)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]], fits[[3]],
          dep.var.labels=c("DX58LeanMassTotPercent"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[4]], fits[[5]], fits[[6]],
          dep.var.labels=c("DX58LeanMassTotPercent"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

```{r, message=FALSE, fig.show="hold"}
do.call(rbind, lapply(fits, function(fit) {
  data.frame(rstd = rstandard(fit), fml = getfml(fit))
})) %>%
  ggplot(aes(sample = rstd)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ fml, ncol = 2) +
  labs(title = "Normal Q-Q plot", x = "Theoretical Quantiles",
       y = "Standardized residuals") +
  theme(strip.text.x = element_text(size = rel(.6)))
```

<!-- ========================= Outcome: DX62_ALMI ========================= -->

## Variable dépendante : `DX62_ALMI`

### Régressions univariables

```{r, fig.show="hold"}
X <- c("TotalWeightLoss", "ExcessWeightLoss", "NadirWeight", "DX03_Age",
       "FollowUpYears")
figs <- lapply(X, function(x) {
  fml <- as.formula(paste("DX62_ALMI ~", x))
  fit <- lm(fml, dta)
  b <- signif(coef(fit)[[2]], 3)
  ci <- signif(confint(fit)[2, ], 3)
  p <- coef(summary(fit))[2, "Pr(>|t|)" ]
  p <- if (p >= 0.001) paste0("p=", round(p, 3)) else "p<0.001"
  r2 <- paste0("R2=", round(summary(fit)$r.squared, 3))
  cap <- paste0("b = ", b, " (", ci[1], ",", ci[2], "), ", p, ", ", r2)
  fig <- ggplot(dta, aes_string(y = "DX62_ALMI", x = x)) +
    geom_point() +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
    labs(caption = cap) +
    theme(axis.title=element_text(size = rel(.75)))
})
do.call(grid.arrange, append(figs, list(nrow = 3)))
rm(X, figs)
```

<!-- ========================= Outcome: DX62_ALMI ========================= -->

### Régressions multivariables - Exposition : `TotalWeightLoss`

```{r}
fits <- list(
  lm(DX62_ALMI ~ TotalWeightLoss_C * NadirWeight_C, dta),
  lm(DX62_ALMI ~ TotalWeightLoss_C * DX03_Age_C, dta),
  lm(DX62_ALMI ~ TotalWeightLoss_C * FollowUpYears_C, dta),
  lm(DX62_ALMI ~ TotalWeightLoss_C + NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX62_ALMI ~ TotalWeightLoss_C * NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX62_ALMI ~ TotalWeightLoss_C * (NadirWeight_C +
       FollowUpYears_C + DX03_Age_C), dta)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]], fits[[3]],
          dep.var.labels=c("DX62ALMI"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[4]], fits[[5]], fits[[6]],
          dep.var.labels=c("DX62ALMI"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

```{r, message=FALSE, fig.show="hold"}
do.call(rbind, lapply(fits, function(fit) {
  data.frame(rstd = rstandard(fit), fml = getfml(fit))
})) %>%
  ggplot(aes(sample = rstd)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ fml, ncol = 2) +
  labs(title = "Normal Q-Q plot", x = "Theoretical Quantiles",
       y = "Standardized residuals") +
  theme(strip.text.x = element_text(size = rel(.6)))
```

<!-- ================== Outcome: DX62_ALMI ================== -->

### Régressions multivariables - Exposition : `ExcessWeightLoss`

```{r}
fits <- list(
  lm(DX62_ALMI ~ ExcessWeightLoss_C * NadirWeight_C, dta),
  lm(DX62_ALMI ~ ExcessWeightLoss_C * DX03_Age_C, dta),
  lm(DX62_ALMI ~ ExcessWeightLoss_C * FollowUpYears_C, dta),
  lm(DX62_ALMI ~ ExcessWeightLoss_C + NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX62_ALMI ~ ExcessWeightLoss_C * NadirWeight_C +
       FollowUpYears_C + DX03_Age_C, dta),
  lm(DX62_ALMI ~ ExcessWeightLoss_C * (NadirWeight_C +
       FollowUpYears_C + DX03_Age_C), dta)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]], fits[[3]],
          dep.var.labels=c("DX62ALMI"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[4]], fits[[5]], fits[[6]],
          dep.var.labels=c("DX62ALMI"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

```{r, message=FALSE, fig.show="hold"}
do.call(rbind, lapply(fits, function(fit) {
  data.frame(rstd = rstandard(fit), fml = getfml(fit))
})) %>%
  ggplot(aes(sample = rstd)) +
  stat_qq() +
  stat_qq_line() +
  facet_wrap(~ fml, ncol = 2) +
  labs(title = "Normal Q-Q plot", x = "Theoretical Quantiles",
       y = "Standardized residuals") +
  theme(strip.text.x = element_text(size = rel(.6)))
```

<!-- ==================== VisceralAdiposeTissue (VAT) ===================== -->

# VisceralAdiposeTissue (VAT)

```{r}
X <- c("T2DPreOp", "HTAPreOp", "DyslipidemiaPreOp", "T2DPostOp",
       "HTAPostOp", "DyslipidemiaPostOp")
do.call(rbind, lapply(X, function(x) {
  i0 <- !is.na(dta$DX55_VAT) & !is.na(dta[[x]]) & dta[[x]] == 0
  i1 <- !is.na(dta$DX55_VAT) & !is.na(dta[[x]]) & dta[[x]] == 1
  u0 <- dta[i0, "DX55_VAT"]
  u1 <- dta[i1, "DX55_VAT"]
  fml <- as.formula(paste("DX55_VAT ~", x))
  data.frame(
    Variable = x,
    N0 = sum(i0),
    Mean0 = mean(u0),
    SD0 = sd(u0),
    N1 = sum(i1),
    Mean1 = mean(u1),
    SD1 = sd(u1),
    ttest.pv = t.test(fml, dta[i0 | i1, ])$p.value,
    wilcox.pv = wilcox.test(fml, dta[i0 | i1, ])$p.value
  )
})) %>%
  kable(digits = 2, row.names = FALSE)
```

```{r, message=FALSE, fig.show="hold"}
dta[c("DX55_VAT", X)] %>%
  gather(variable, value, -DX55_VAT) %>%
  mutate(variable = factor(variable, X)) %>%
  ggplot(aes(x = factor(value), y = DX55_VAT)) +
  geom_boxplot() +
  facet_wrap(~variable) +
  labs(x = "")
dta[c("DX55_VAT", X)] %>%
  gather(variable, value, -DX55_VAT) %>%
  mutate(variable = factor(variable, X), value = factor(value)) %>%
  ggplot(aes(x = DX55_VAT, group = value, color = value)) +
  stat_ecdf(geom = "step") +
  facet_wrap(~variable) +
  labs(y = "Probability",
       title = "Empirical cumulative distribution functions") +
  theme(legend.title = element_blank())
rm(X)
```

```{r, message=FALSE, fig.show="hold"}
tmp <- dta %>% mutate(
  T2DPreOp = factor(T2DPreOp),
  T2DPostOp = factor(T2DPostOp)
)
aes_list <- list(
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent),
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent, color = T2DPreOp),
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent, color = T2DPostOp)
)
figs <- lapply(aes_list, function(aes_element) {
  ggplot(tmp, aes_element) +
    geom_point() +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
    theme(legend.position="top")
})
do.call(grid.arrange, append(figs, list(ncol = 2)))
rm(tmp, aes_list, figs)
```

```{r}
fits <- list(
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C, dta),
  lm(DX55_VAT ~ T2DPreOp, dta),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C + T2DPreOp, dta),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C * T2DPreOp, dta),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C, dta),
  lm(DX55_VAT ~ T2DPostOp, dta),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C + T2DPostOp, dta),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C * T2DPostOp, dta)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[3]], fits[[4]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[5]], fits[[6]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[7]], fits[[8]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}



<!-- =========== VisceralAdiposeTissue (VAT) without Dx00000149 =========== -->

# VisceralAdiposeTissue (VAT) without Dx00000149

```{r}
dta2 <- dta[dta$Id != "Dx00000149", ]
X <- c("T2DPreOp", "HTAPreOp", "DyslipidemiaPreOp", "T2DPostOp",
       "HTAPostOp", "DyslipidemiaPostOp")
do.call(rbind, lapply(X, function(x) {
  i0 <- !is.na(dta2$DX55_VAT) & !is.na(dta2[[x]]) & dta2[[x]] == 0
  i1 <- !is.na(dta2$DX55_VAT) & !is.na(dta2[[x]]) & dta2[[x]] == 1
  u0 <- dta2[i0, "DX55_VAT"]
  u1 <- dta2[i1, "DX55_VAT"]
  fml <- as.formula(paste("DX55_VAT ~", x))
  data.frame(
    Variable = x,
    N0 = sum(i0),
    Mean0 = mean(u0),
    SD0 = sd(u0),
    N1 = sum(i1),
    Mean1 = mean(u1),
    SD1 = sd(u1),
    ttest.pv = t.test(fml, dta2[i0 | i1, ])$p.value,
    wilcox.pv = wilcox.test(fml, dta2[i0 | i1, ])$p.value
  )
})) %>%
  kable(digits = 2, row.names = FALSE)
```

```{r, message=FALSE, fig.show="hold"}
dta2[c("DX55_VAT", X)] %>%
  gather(variable, value, -DX55_VAT) %>%
  mutate(variable = factor(variable, X)) %>%
  ggplot(aes(x = factor(value), y = DX55_VAT)) +
  geom_boxplot() +
  facet_wrap(~variable) +
  labs(x = "")
dta2[c("DX55_VAT", X)] %>%
  gather(variable, value, -DX55_VAT) %>%
  mutate(variable = factor(variable, X), value = factor(value)) %>%
  ggplot(aes(x = DX55_VAT, group = value, color = value)) +
  stat_ecdf(geom = "step") +
  facet_wrap(~variable) +
  labs(y = "Probability",
       title = "Empirical cumulative distribution functions") +
  theme(legend.title = element_blank())
rm(X)
```

```{r, message=FALSE, fig.show="hold"}
tmp <- dta2 %>% mutate(
  T2DPreOp = factor(T2DPreOp),
  T2DPostOp = factor(T2DPostOp)
)
aes_list <- list(
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent),
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent, color = T2DPreOp),
  aes(y = DX55_VAT, x = DX59_FatMassTotPercent, color = T2DPostOp)
)
figs <- lapply(aes_list, function(aes_element) {
  ggplot(tmp, aes_element) +
    geom_point() +
    geom_smooth(method = lm, formula = y ~ x, se = FALSE) +
    theme(legend.position="top")
})
do.call(grid.arrange, append(figs, list(ncol = 2)))
rm(tmp, aes_list, figs)
```

```{r}
fits <- list(
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C, dta2),
  lm(DX55_VAT ~ T2DPreOp, dta2),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C + T2DPreOp, dta2),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C * T2DPreOp, dta2),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C, dta2),
  lm(DX55_VAT ~ T2DPostOp, dta2),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C + T2DPostOp, dta2),
  lm(DX55_VAT ~ DX59_FatMassTotPercent_C * T2DPostOp, dta2)
)
```

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[1]], fits[[2]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[3]], fits[[4]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[5]], fits[[6]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

\begin{center}
```{r, echo=FALSE, results='asis'}
stargazer(fits[[7]], fits[[8]],
          dep.var.labels=c("DX55VAT"), single.row=TRUE,
          float = FALSE, header = FALSE, intercept.bottom = FALSE,
          intercept.top = TRUE, model.numbers = FALSE)
```
\end{center}

